Light versus Dark in Strong Lensing Galaxies: Dark matter halos are rounder than their stars

### 2014-12-22 shapes/paper.tex
Added missing Sections, changed wedges Figures and generally worked on the paper

Recently, we introduced a new non-parametric lens tool, \Glass\  \citep{2014arXiv1401.7990C}. Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass dominates the potential over the region of the images. {\bf CB. i) is the case for all the lenses, ii) however only for a minority of the sample. This sentence creates therefore some tension that is not addressed however (I don't know whether we should rephrase it or add another sentence).} In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies. We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time. This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter. Since the stars often dominate the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution. Our comparison between light and dark is made possible by the fact that \Glass\ uses the light distribution as a prior on the mass map, ensuring that the dark matter mass is always positive.

@@

\Glass{} is a new `non-parametric' gravitational lens modelling framework
\citep{2014arXiv1401.7990C} that is capable of generating a distribution of
mass models given a set of basic assumptions, or priors.  In this context,
non-parametric means that  many more parameters than data constraints are used
such that system of equations describing the lensing mass distribution is
under-constrained.  \Glass{} shares some aspects with an earlier code
\PixeLens{} \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely
different code base. Its key improvements upon \PixeLens{} which are relevant
for this paper include:

@@

%\Glass{} is described in detail in the code paper: \citet{2014arXiv1401.7990C}.
In this paper, the default priors used to model each lens are listed below.  Table
\ref{tab:lensmodelling} identifies lenses for which we have modified these defaults.
For each lens we assume:

\begin{enumerate} 
\item Observational priors (redshifts, image positions relative to lens position).
\item Image parity is enforced.
\item A reconstructed stellar mass map.
\item The local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
\item The fixed cosmology $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
\end{enumerate}

@@

\subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}

{\bf JR. WE NEED TO DEFINE OUR SHAPE PARAMETER AND ANALYSIS METHOD HERE.} 
{\bf JR. WE NEED TO ALSO DEFINE $R_e$ HERE AND EXPLAIN THAT WE AVERAGE SHAPE OVER 1-5$R_e$} 
{\bf CB. I will write this.}

\section{Data}\label{sec:data}

{\bf CB. Do we need to add a bit describing the stellar population synthesis modelling? Can maybe Prasenjit write this?}

\textit{Q0047-2808} (hereafter \textit{Q0047} or \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}. \cite{2011ApJ...726...84W} find a group of 9 members all of which are spectroscopically confirmed.

\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}. \cite{1993AJ....105....1S} find a very close luminous satellite galaxy north-west of the lens. \citep{2011MNRAS.413L..86C} however conclude that it is more likely a foreground object.

\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}. %Another galaxy, 102'' to the south-east seems to be at a similar redshift \citep{2002AJ....123..627F}. There is also a group of 10 galaxies at a lower redshift.

\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}. It has measured time delays \citep{2002ApJ...572L..11H}. It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}. X-ray emission can be detected and an analysis of which yields a temperature of 2.3 keV. There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}. %This cluster seems to be rather complex and especially it is not spherical. Possibly it is not dynamically relaxed, although X-ray emission can be detected.

\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction (e.g. \cite{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}). Due to the large image separation, large physical scales are probed. As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east. These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}. The lens has a measured time delay, e.g. \citep{2012A&A...540A.132S}. They however also find a three-day lag between the g- and r-bands, and the estimates do not agree at the 2$\sigma$-level. They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion. We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.

\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}. It has measured time delays. We use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} which differ from previously found values by e.g. \cite{1997ApJ...489...21B}. \cite{2006ApJ...641..169M} and \cite{2011ApJ...726...84W} analyzed the environment of the lens thouroughly. It is part of a small group of 13 members. \cite{2004ApJ...610..686G} detect also X-ray emission from the corresponding group, which yields a temperature of 0.8 keV.

\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}. Although there are measured time delays by \cite{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations in \cite{2003AJ....126...29R}. We choose therefore not to include them in the analysis. \cite{2006ApJ...641..169M} find a group environment with 16 spectroscopically confirmed member galaxies. Using newer data, \cite{2011ApJ...726...84W} find an additional member. \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.

\textit{B1608+656} (hereafter \textit{1608} or \textit{1608}) consists of two merging galaxies. The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}. The system has measured time delays \citep{2002ApJ...581..823F}. The environment and the mass distribution along the line of sight have been analyzed by \cite{2006ApJ...642...30F}. They find a group with 8 (9 if merging galaxies are counted individually). No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}. The data seems to indicate four other groups along the line of sight.

@@

\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}. \cite{1999AJ....117..658F} initially classified the galaxy as a late-type Sa galaxy, the velocity dispersion however seems too high. As the source redshift is rather low, a large lens mass is required. \cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy. To the west of the lens, \cite{1999AJ....117..658F} find a group at a similar redshift as the lens. \cite{2007MNRAS.378..109M} also find evidence for a dwarf satellite galaxy. As the measurements are inconclusive, we choose to not include this satellite.

\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}. With only a redshift of $z=0.04$, it is the closest lens of the sample. Due to the low redshift, the probed physical scales are small. No further inquiries into the environment were made.

Further information about the sample can be found in \cite{leier11phd}, \cite{2011ApJ...740...97L}, and \cite{2012A&A...538A..99S}.

\begin{table*}
  \begin{center}
    \begin{tabular}{l r r r r l}
      Lens    & \multicolumn{1}{c}{$z_{L}$} & \multicolumn{1}{c}{$z_{S}$} & \multicolumn{1}{c}{$\Delta\theta$ [kpc]} & \multicolumn{1}{c}{$R_{L}$/$R_{e}$} & Environment \\ \hline
      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9) \\
      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... \\
      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... \\
      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C \\
      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C \\
      1115 & 0.310 & 1.72 & 10.76 & $2.94\pm0.06$ & G(13) \\
      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17) \\
      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8) \\
      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69) \\
      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... \\
      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... \\
    \end{tabular}
    \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}. References can be found in \S\ref{sec:data}.}
    \label{tab:lensproperties}
  \end{center}
\end{table*}

\begin{table*}
  \begin{center}
    \begin{tabular}{l r r r r l l}
      Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
      0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & \\
           & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
      0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & \\
           & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
           & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
      0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
           & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
      0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
           & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
      1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
           & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
      1422 & 1.079 & 0.357 & 0.742 & -0.205 & ... & Symm \\
           & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
      1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & \\
           & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
      2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & \\
           & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
      2045 & 1.121 & 1.409 & 1.255 & -0.507 & ... & $\gamma(0.1)$, Symm \\
           & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
      2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & \\
              & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
    \end{tabular}
    \caption[width=\linewidth]{The lens properties relevant for modelling the lenses are listed (positions and time delay information). The images are ordered in terms of arrival time (image A has the shortest arrival time, image D the longest). \newline $^{a}$ The source lensed by 0957 has different component. Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
    \label{tab:lensmodelling}
  \end{center}
\end{table*}

\section{Results}\label{sec:results}

{\bf JR. CLAUDIO OR JUSTIN TO WRITE RESULTS SECTION?} 
\textbf{Content:}
\begin{itemize}
\item Describe special features in reconstructed lenses
\item Show the wedges money plot
\item Discuss the results, especially:
\item 1. Dark matter halos seem quite round, stars not necessarily
\item 2. Both DM and stars more elliptical with increasing radius 
\item 3. DM halos with weak shear are aligned (apart from spherical systems that don't count); strong shear systems can be highly misaligned.
\item 4. No sensitivity to shear prior. Only one lens B2045 requires a shear prior to avoid spurious extra images; doesn't affect the shape measure though. 
\item 5. Merger systems stand out. 
\end{itemize}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{Figures/wedges_shears.pdf}
  \caption[width=.65\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$. The wedges display the alignment of the semi-major axes of the components. In case of alignment of the semi-major axes (Aligned), the wedges are vertical. In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal. The opening angle displays the error in the shape estimate of the dark matter halo. The lenses are additional color-coded in terms of the required external shear in modelling the lens.}
  \label{fig:wedges}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
  \caption[width=.65\linewidth]{Similar to Figure~\ref{fig:wedges}. In each of the subfigures however we only consider pixels within 1, 2, 3, 4, or 5 $R_e$. If a lens does not extend to these limiting radii, it is dropped from the analysis in this and subsequent subfigures.}
  \label{fig:wedgesall}
\end{figure*}

\section{Conclusion}\label{sec:conclusions}

We have measured the shape and alignment of stars and dark matter in 11 strong lensing galaxies using a new non-parametric lens tool, \Glass. We focussed on lenses that have either time delay data or stellar mass maps that contribute significantly to the central potential, since these have data quality good enough to determine the projected shape of their dark matter halos \citep{2014arXiv1401.7990C}. We measured the shape and alignment using the eigenvalues $\lambda$ and vectors of the 2D moment of inertia tensor of the stars and dark matter, defining a {\it shape parameter} $s = \lambda_{\rm max}/\lambda_{\rm min}$ (\S\ref{sec:shapemethod}). We averaged $s$ over the range 1-5$R_e$, where $R_e$ is the effective radius of the light profile.

>>>>

Recently, we introduced a new non-parametric lens tool, \Glass\ \citep{2014arXiv1401.7990C}. Applying this to a large suite of mock data, we showed that mass and light can only reliably be disentangled in strong lensing systems if: i) there are at least four images; and ii) time delay data are available and/or the stellar mass dominates the potential over the region of the images. {\bf (CB. i) is the case for all the lenses except Q0957, ii) however is only the case for a minority of the sample. This sentence creates therefore some tension that is not addressed however (I don't know whether we should rephrase it or add another sentence))} In this paper, we collate data of the above quality, compiling a sample of 11 strong lens galaxies. We apply \Glass\ to these lenses to non-parametrically measure the shape and alignment of the stars and {\it dark matter}  in these lensing galaxies, for the first time. This differs from previous works that have all compared the light distribution with the total mass, rather than the dark matter. Since the stars often dominate the central potential, the total mass naturally correlates with the light, potentially masking theoretically interesting results about the dark matter distribution. Our comparison between light and dark is made possible by the fact that \Glass\ uses the light distribution as a prior on the mass map, ensuring that the dark matter mass is always positive.

@@

\Glass{} is a new `non-parametric' gravitational lens modelling framework
\citep{2014arXiv1401.7990C} that is capable of generating a distribution of
mass models given a set of basic assumptions, or priors.  {\bf Hence, \Glass\ does not yield the most probable mass model. Rather, we can describe the distribution of all the allowed models. (CB: I'VE ADDED THIS SENTENCE AS I FELT SOMETHING LIKE THAT MIGHT BE NEEDED AT THIS POINT. IT PROBABLY NEEDS TO BE IMPROVED THOUGH)} In this context,
non-parametric means that  many more parameters than data constraints are used
such that system of equations describing the lensing mass distribution is
under-constrained.  \Glass{} shares some aspects with an earlier code
\PixeLens{} \citep{2004AJ....127.2604S,2008ApJ...679...17C}, but has a completely
different code base. Its key improvements upon \PixeLens{} which are relevant
for this paper include:

@@

%\Glass{} is described in detail in the code paper: \citet{2014arXiv1401.7990C}.
In this paper, the default priors used to model each lens are listed below.  Table
\ref{tab:lenspriors} identifies lenses for which we have modified these defaults.
For each lens we assume:

\begin{enumerate} 
\item Observational priors (redshifts, image positions relative to lens position).
\item Image parity is enforced.
\item A reconstructed stellar mass map as lower mass bounds in every pixel.
\item The local density gradient is always pointing within 50$^{\circ}$ to the center and the slope is at most 0 everywhere. In other words, the density profile peaks in the center.
\item The fixed cosmology $\Omega_{m} = 0.28$, $\Omega_{\Lambda} = 0.72$, $\Omega_{k} = 0$, $H_{0}^{-1} = 13.7$ Gyr.
\item A flat prior on the magnitude of the external shear $|\gamma|$ on $[0,1)$.
\end{enumerate}

@@

\subsection{Measuring the shape and alignment of a lens}\label{sec:shapemethod}
We employ the same shape definition as in \citep{2014arXiv1401.7990C}. The shape parameter $s$ is defined as the ratio of the two eigenvalues $\lambda_1$ and $\lambda_2$, i.e.
\begin{equation}\label{eq:shapeestimate}
    s \equiv \frac{\lambda_{1}}{\lambda_{2}}, \ \ \ \mathrm{where} \ \lambda_{1} \geq \lambda_{2},
\end{equation}
of the inertia tensor of a mass distribution $M(\boldsymbol{\theta})$
\begin{equation}\label{eq:inertiatensor}
    I = \begin{pmatrix} \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{y} & -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} \\
                        -\sum_\theta M(\boldsymbol{\theta})\theta_{x}\theta_{y} & \sum_\theta M(\boldsymbol{\theta})\theta^{2}_{x} \end{pmatrix}.
\end{equation}
We use these estimators to quantify the shape of the stellar mass distribution and the dark matter distribution. We estimate the latter by reconstructing the total mass distribution with a lower mass prior from the stellar mass distribution and then subtracting the latter off. The shapes of the distributions are computed for all the pixels up to the outermost lensed image and for the pixels within different multiples of the half-light radius $R_e$. $R_e$ is the Petrosian radius containing half of the flux of the total light distribution. As terms in Eq.~\ref{eq:inertiatensor} are weighted with $r^2$, the outer pixels tend to dominate the estimate of the averaged shape within the considered radius. The shape estimates do not necessarily need to be the same within different radii. E.g. there are effects as isophotal twist \citep[e.g.][and references therein]{1978ComAp...8...27B} causing differences in the shape estimates between the central and the outer parts of the system. {\bf (CB: THESE LAST SENTENCES PROBABLY NEED TO BE REPHRASED TOO)}

Throughout this paper, we consider only the masses in the pixels up to one pixel length past the outermost image. Furthermore, we generate 10000 mass models for each system we consider and describe the distribution of all the individual estimates for the dark matter shapes. {\bf (CB: MAYBE NEEDS REPHRASING, SEE ABOVE)}

\section{Data}\label{sec:data}
Stellar-mass maps are taken from \citep{2011ApJ...740...97L}.  In that work, the light of the galaxy images in all available HST bands was first fitted using using GALFIT \citep{2002AJ....124..266P}, and the resulting light maps were used to obtain stellar-mass maps using a synthesis of the stellar-population models of \citep{2003MNRAS.344.1000B}.  The population synthesis marginalised over the star-formation epoch and time scales and over the stellar metallicity.  The IMF was taken to be the log-normal form given by \citep{2003PASP..115..763C}; a more bottom-heavy IMF would change the mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the inferred shape of the stellar mass.

As it is shown in \citep{2014arXiv1401.7990C}, the recovery of the shape information of the lens is only good if there are at least four images. Therefore, we only consider the quad lenses and the twin double \textit{Q0957+561} out of the sample presented in \citep{2011ApJ...740...97L}. Thus, the sample consists in total of 11 lenses. Each individual system is presented below.

\textit{Q0047-2808} (hereafter \textit{0047}) is a luminous early-type galaxy \citep{1996MNRAS.278..139W}. It is part a group of 9 members, all of which are spectroscopically confirmed \citep{2011ApJ...726...84W}.

\textit{MG0414+0534} (hereafter \textit{0414}) is a passively evolving early-type galaxy \citep{1999AJ....117.2034T}. A very close luminous satellite galaxy was found north-west of the lens \citep{1993AJ....105....1S}. It however is more likely a foreground object \citep{2011MNRAS.413L..86C}.

\textit{B0712+472} (hereafter \textit{0712}) is an early-type galaxy \citep{1998AJ....115..377F}.

\textit{RXJ0911+0551} (hereafter \textit{0911}) is an almost circular early-type galaxy \citep{2012A&A...538A..99S}. It has measured time delays \citep{2002ApJ...572L..11H}. It lies on the outskirts of a cluster \citep{2001ApJ...555....1M}. X-ray emission can be detected and an analysis of which yields a temperature of 2.3 keV. There is also a satellite galaxy to the north-west direction \citep{2000ApJ...544L..35K}.

\textit{Q0957+561} (hereafter \textit{0957}) is a cD galaxy lying close to the center of a cluster with a high sprial galaxy-fraction \citep[e.g.][]{1992MNRAS.254P..27G,1994A&A...291..411A,1998ApJ...504..661C}. Due to the large image separation, large physical scales are probed. As listed in Table 3 of \cite{2000ApJ...542...74K}, the position angles to the center of the cluster of earlier lens reconstructions range between 51.8 deg and 67.8 deg measured north-through-east. These results are consistent with the center of the X-ray emission from the cluster \citep{1998ApJ...504..661C}. The lens has a measured time delay \citep[e.g.][]{2012A&A...540A.132S}. They however also find a three-day lag between the g- and r-bands, a disagreement at the 2$\sigma$-level. They argue that this effect can be accounted for by the presence of a substructure and chromatic dispersion. We find that the results do not change significantly for either estimate and choose therefore the g-band measurement.

\textit{PG1115+080} (hereafter \textit{1115}) is an early-type galaxy \citep{2005ApJ...626...51Y}. It has measured time delays. In this work use recent estimates of the time delays by \cite{2010MNRAS.406.2764T} that differ from previously found values by e.g. \cite{1997ApJ...489...21B}. The environment of the lens was analyzed thouroughly \citep{2006ApJ...641..169M,2011ApJ...726...84W}. It is part of a small group of 13 members. Also X-ray emission was detected from the corresponding group, and it yields a temperature of 0.8 keV \citep{2004ApJ...610..686G}.

\textit{B1422+231} (hereafter \textit{1422}) is an early-type galaxy \citep{1996ApJ...462L..53I}. Although there are measured time delays \citep{2001MNRAS.326.1403P}, they seem to deviate significantly from theoretical expectations \citep{2003AJ....126...29R}. We choose therefore not to include them in the analysis. The lens is part of a group with 16 spectroscopically confirmed member galaxies \citep{2006ApJ...641..169M}. Using newer data, an additional member could be found \citep{2011ApJ...726...84W}. \cite{2004ApJ...610..686G} also detect X-ray emission from the corresponding group at a temperature of 1.0 keV.

\textit{B1608+656} (hereafter \textit{1608}) consists of two merging galaxies. The main galaxy is an early-type galaxy which is disrupted by a smaller, probably late-type galaxy \citep{2003ApJ...584..100S}. The system has measured time delays \citep{2002ApJ...581..823F}. The environment has been analyzed and group with 8 (9 if merging galaxies are counted individually) was found \citep{2006ApJ...642...30F}. No significant X-ray emission was detected from the surrounding group \citep{2005ApJ...625..633D}. The data seems to indicate four other groups along the line of sight.

@@

\textit{B2045+265} (hereafter \textit{2045}) is probably an elliptical galaxy \citep{2007MNRAS.378..109M}. It was initially classified as a late-type Sa galaxy \citep{1999AJ....117..658F}, the velocity dispersion however seems too high. As the source redshift is rather low, a large lens mass is required. \cite{2007MNRAS.378..109M} therefore conclude that it is more likely an elliptical galaxy. To the west of the lens, a group was found at a similar redshift as the lens \citep{1999AJ....117..658F}. There is furthermore evidence for a dwarf satellite galaxy \citep{2007MNRAS.378..109M}. As the measurements are inconclusive, we choose to not include this satellite.

\textit{Q2237+030} (hereafter \textit{2237}) is a barred spiral \citep{1988AJ.....95.1331Y}, the only non-early type lens in this sample. With only a redshift of $z=0.04$, it is the closest lens of the sample. Due to the low redshift, the probed physical scales are small. Therefore, the bulge component of the galaxy dominates the lens, what makes the stellar population synthesis modelling possible. No further inquiries into the environment were made. It is

Further information on the sample can be found in \citep{2011ApJ...740...97L,2012A&A...538A..99S}. The most important quantities of each system are given in Table~\ref{tab:lensproperties}. Due to the different angular separations of the images, different scales of the lens galaxies are probed.

\begin{table}
  \begin{center}
    \begin{tabular}{l r r r r l}
      Lens    & \multicolumn{1}{c}{$z_{L}$} & \multicolumn{1}{c}{$z_{S}$} & \multicolumn{1}{c}{$\Delta\theta$ [kpc]} & \multicolumn{1}{c}{$R_{L}$/$R_{e}$} & Environment \\ \hline
      0047 & 0.485 & 3.60 & 12.82 & $1.45\pm0.04$ & G(9) \\
      0414 & 0.960 & 2.64 & 16.01 & $1.85\pm0.05$ & ... \\
      0712 & 0.410 & 1.34 & 6.82  & $1.15\pm0.03$ & ... \\
      0911 & 0.769 & 2.8  & 23.16 & $3.09\pm0.05$ & C \\
      0957 & 0.356 & 1.41 & 29.98 & $3.51\pm0.04$ & C \\
      1115 & 0.310 & 1.72 & 10.76 & $2.86\pm0.06$ & G(13) \\
      1422 & 0.337 & 3.62 & 6.02  & $4.49\pm0.06$ & G(17) \\
      1608 & 0.630 & 1.39 & 13.92 & $1.82\pm0.01$ & G(8) \\
      2016 & 1.010 & 3.3  & 26.22 & $6.12\pm0.14$ & C(69) \\
      2045 & 0.870 & 1.28 & 14.46 & $1.48\pm0.03$ & ... \\
      2237 & 0.039 & 1.7  & 1.40  & $0.89\pm0.01$ & ... \\
    \end{tabular}
    \caption[width=\linewidth]{The most relevant lens properties for this work are listed \citep[for an expanded version of this table see][]{2011ApJ...740...97L}. References can be found in \S\ref{sec:data}. The columns are from left to right, the lens redshift $z_L$, the redshift of the source $z_S$, the maximum angular separation between two images $\Delta\theta$, the ratio of the radius of the outermost image $R_L$ and the effective Petrosian half-light radius of the lens $R_e$, and information on the environment of the lens. C and G denote a known cluster resp. group environment. The number in the brackets is the number of confirmed members.}
    \label{tab:lensproperties}
  \end{center}
\end{table}

% \begin{table*}
%   \begin{center}
%     \begin{tabular}{l r r r r l l}
%       Lens    & \multicolumn{1}{c}{A ['']} & \multicolumn{1}{c}{B ['']} & \multicolumn{1}{c}{C ['']} & \multicolumn{1}{c}{D ['']} & Time delays [days] & Additional priors \\ \hline
%       0047 & 1.270 & -0.630 & 0.520 & -0.730 & ... & \\
%            & 0.105 & -0.995 & -1.045 & 0.705 & &  \\
%       0414 & -0.472 & -1.061 & -1.1947 & 0.885 & ... & \\
%            & 1.277 & -0.661 & -0.255 & -0.361 & &  \\
%       0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
%            & -0.804 & -0.156 & -0.292 & 0.307 & &  \\
%       0712 & -0.013 & 0.795 & 0.747 & -0.391 & ... & \\
%            & -0.804 & -0.156 & -0.292 & 0.307 &  &  \\
%       0957$^{a}$ & 1.408 & 0.182 & 2.860 & -1.540 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
%            & 5.034 & -1.018 & 3.470 & -0.050 &  &  \\
%       1115 & 0.355 & -0.909 & -1.093 & 0.717 & $\Delta t_{BA}=12.0^{+2}_{-2} \ \Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
%            & 1.322 & -0.714 & -0.260 & -0.627 & &  \\
%       1422 & 1.079 & 0.357 & 0.742 & -0.205 & ... & Symm \\
%            & -0.095 & 0.973 & 0.656 & -0.147 &  &  \\
%       1608 & -1.300 & -0.560 & -1.310 & 0.570 & $\Delta t_{BA}=31.5^{+2}_{-1} \ \Delta t_{CA}=36.0^{+1.5}_{-1.5} \ \Delta t_{DA}=77.0^{+2}_{-1}$ & \\
%            & -0.800 & 1.160 & 0.700 & -0.080 &  &  \\
%       2016 & -1.735 & 0.335 & 0.437 & 1.268 & ... & \\
%            & 1.778 & -1.450 & -1.435 & 0.276 &  &  \\
%       2045 & 1.121 & 1.409 & 1.255 & -0.507 & ... & $\gamma(0.1)$, Symm \\
%            & 0.824 & 0.035 & 0.576 & -0.183 &  &  \\
%       2237 & 0.598 & -0.075 & 0.791 & -0.710 & ... & \\
%               & 0.758 & -0.939 & -0.411 & 0.271 &  &  \\
%     \end{tabular}
%     \caption[width=\linewidth]{The lens properties relevant for modelling the lenses are listed (positions and time delay information). The images are ordered in terms of arrival time (image A has the shortest arrival time, image D the longest). \newline $^{a}$ The source lensed by 0957 has different component. Images A and B are a double associated with the main galaxy component, images C and D are associated with lensed substructure.}
%     \label{tab:lensmodelling}
%   \end{center}
% \end{table*}
\begin{table}
  \begin{center}
    \begin{tabular}{l l l}
      Lens & Time delays [days] & Additional priors \\ \hline
      0047 & ... & ...\\
      0414 & ... & ...\\
      0712 & ... & ...\\
      0712 & ... & ...\\
      0957 & $\Delta t_{BA}=416.5^{+1}_{-1}$ & Symm \\
      1115 & $\Delta t_{BA}=12.0^{+2}_{-2}$ & ...\\
           & $\Delta t_{DC}=4.4^{+3.2}_{-2.4}$ & \\
      1422 & ... & Symm \\
      1608 & $\Delta t_{BA}=31.5^{+2}_{-1}$ & ...\\
           & $\Delta t_{CA}=36.0^{+1.5}_{-1.5}$ & \\
           & $\Delta t_{DA}=77.0^{+2}_{-1}$ & \\
      2016 & ... & ...\\
      2045 & ... & $\gamma(0.1)$, Symm \\
      2237 & ... & ...\\
    \end{tabular}
    \caption[width=\linewidth]{Additional priors to the baseset described in \S\ref{sec:glass} are listed. $\Delta t_{BA}$ denotes the difference in arrival time $t_{B}-t_{A}$. The images are defined in Table~\ref{tab:lenspositions}. $\gamma(\cdot)$ denotes a prior on the maximum allowed external shear $|\gamma|$. Symm denotes that a point-symmetry prior is employed.}
    \label{tab:lenspriors}
  \end{center}
\end{table}

\section{Results}\label{sec:results}
\begin{figure*}
  \centering
  \includegraphics[width=.8\linewidth]{Figures/wedges_shears.pdf}
  \caption[width=\linewidth]{The reconstructed lenses are displayed according to the reconstructed total shapes of the dark matter halo $s_{dm}$ and the stellar component $s_{*}$. The wedges display the alignment of the semi-major axes of the components. In case of alignment of the semi-major axes (Aligned), the wedges are vertical. In case of alignment of the semi-major with the semi-minor axes (Anti-Aligned), the wedges are horizontal. The opening angle displays the statiscal error in the shape estimate of the dark matter halo. Both the error in the alignment and the ellipticity of the dark matter distribution denote the ranges $68\%$ of all the mass models lie within. The lenses are additionally color-coded in terms of the required external shear in modelling the lens.}
  \label{fig:wedgesall}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=.8\linewidth]{Figures/wedges.pdf}
  \caption[width=\linewidth]{Similar to Figure~\ref{fig:wedgesall}. In each of the subfigures however we only consider pixels within 1, 2, 3, 4, or 5 $R_e$. If the outermost image of a system lies within one of the limiting radii, the system is kept in this panel, but dropped from subsequent panels.}
  \label{fig:wedgesradii}
\end{figure*}

{\bf (CB: In general, do we need to link the results better to previous studies? We mention them already in the introduction and since they're not directly comparable, I'm not sure how much emphasis should be put on the comparison.)}

We have applied \Glass\ to the data set described in \S\ref{sec:data} consisting of 11 lenses. The reconstructed mass maps and the in this work used stellar mass maps \citep{2011ApJ...740...97L} are displayed in the Appendix.

Figure~\ref{fig:wedgesall} displays the shapes (see \S\ref{sec:shapemethod}) and their alignment of the dark and stellar mass distribution. In this Figure all the distribution up to the last-image radius $R_{L}$ are probed. Different features are evident. First, the reconstructed dark matter distribution of the considered lenses is rounder than the stellar distribution. Second, most lenses are in the bottom-left corner. Thus, the dark matter distributions are typically quite round, while the stellar distributions can be rather elliptical. {\bf HERE MAYBE SOME SENTENCES HOW THIS RESULT IS SURPRISING}

Third, 3 out of the 11 systems, {\it0712}, {\it2016}, and {\it1608}, stand out due to the larger stellar ellipticity ($s_* > 1.6$) and at the same time an alignment of the dark matter and stellar distributions. One of those lenses, {\it1608}, is an known merger of an early-type galaxy with a probably late-type galaxy \citep{2003ApJ...584..100S}. We suggest that the other two systems, {\it0712} and {\it2016}, may be post-merger systems as well and therefore display those similarities with {\it1608}.
